Evaluating Variable Importances

### 2019-04-21 Scripts/distribution_of_tads.Rmd
editted results scripts

>>>>

#Both cell lines together

##10kb

```{r}
tad_gm12878_10kb <- read.table("Z:/TAD_data_analysis/GM12878/10kb/GM12878_domain_data_10000.b.txt")
tad_gm12878_10kb <- tad_gm12878_10kb[,1:3]
tad_gm12878_10kb <- tad_gm12878_10kb %>%
  group_by(V1) %>%
  mutate(Length = V3-V2)
tad_gm12878_10kb$V1 <- factor(tad_gm12878_10kb$V1, levels = c(1:22))
tad_data_gm12878_10kb <- tad_gm12878_10kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1)) 
tad_data_gm12878_10kb$CL <- "GM12878"

tad_K562_10kb <- read.table("Z:/TAD_data_analysis/K562/10kb/K562_domain_data_10000.b.txt")
tad_K562_10kb <- tad_K562_10kb[,1:3]
tad_K562_10kb <- tad_K562_10kb %>%
  group_by(V1) %>%
  mutate(Length = V3-V2)
tad_K562_10kb$V1 <- factor(tad_K562_10kb$V1, levels = c(1:22))
tad_data_K562_10kb <- tad_K562_10kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1))
tad_data_K562_10kb$CL <- "K562"

tad_data_10kb <- rbind.data.frame(tad_data_gm12878_10kb, tad_data_K562_10kb)
tad_data_10kb$CL <- factor(tad_data_10kb$CL, levels=c("GM12878", "K562"))

p_tadnum_10kb <- ggplot(tad_data_10kb, aes(x=V1, y=Count, fill=CL))+
  geom_bar(stat="identity") +
  scale_fill_discrete(name="Cell Line") +
  #guides(fill=FALSE) +
  #ylab("Number of TADs") +
  #xlab("Chromosome") +
  ylab("") +
  xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

##25kb

```{r}
tad_gm12878_25kb <- read.table("Z:/TAD_data_analysis/GM12878/25kb/GM12878_domain_data_25000.b.txt")
tad_gm12878_25kb <- tad_gm12878_25kb[,1:3]
tad_gm12878_25kb <- tad_gm12878_25kb %>%
  group_by(V1) %>%
  mutate(Length = V3-V2)
tad_gm12878_25kb$V1 <- factor(tad_gm12878_25kb$V1, levels = c(1:22))
tad_data_gm12878_25kb <- tad_gm12878_25kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1)) 
tad_data_gm12878_25kb$CL <- "GM12878"

tad_K562_25kb <- read.table("Z:/TAD_data_analysis/K562/25kb/K562_domain_data_25000.b.txt")
tad_K562_25kb <- tad_K562_25kb[,1:3]
tad_K562_25kb <- tad_K562_25kb %>%
  group_by(V1) %>%
  mutate(Length = V3-V2)
tad_K562_25kb$V1 <- factor(tad_K562_25kb$V1, levels = c(1:22))
tad_data_K562_25kb <- tad_K562_25kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1))
tad_data_K562_25kb$CL <- "K562"

tad_data_25kb <- rbind.data.frame(tad_data_gm12878_25kb, tad_data_K562_25kb)
tad_data_25kb$CL <- factor(tad_data_25kb$CL, levels=c("GM12878", "K562"))

p_tadnum_25kb <- ggplot(tad_data_25kb, aes(x=V1, y=Count, fill=CL))+
  geom_bar(stat="identity") +
  scale_fill_discrete(name="Cell Line") +
  #guides(fill=FALSE) +
  #ylab("Number of TADs") +
  #xlab("Chromosome") +
  ylab("") +
  xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

##50kb

```{r}
tad_gm12878_50kb <- read.table("Z:/TAD_data_analysis/GM12878/50kb/GM12878_domain_data_50000.b.txt")
tad_gm12878_50kb <- tad_gm12878_50kb[,1:3]
tad_gm12878_50kb <- tad_gm12878_50kb %>%
  group_by(V1) %>%
  mutate(Length = V3-V2)
tad_gm12878_50kb$V1 <- factor(tad_gm12878_50kb$V1, levels = c(1:22))
tad_data_gm12878_50kb <- tad_gm12878_50kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1)) 
tad_data_gm12878_50kb$CL <- "GM12878"

tad_K562_50kb <- read.table("Z:/TAD_data_analysis/K562/50kb/K562_domain_data_50000.b.txt")
tad_K562_50kb <- tad_K562_50kb[,1:3]
tad_K562_50kb <- tad_K562_50kb %>%
  group_by(V1) %>%
  mutate(Length = V3-V2)
tad_K562_50kb$V1 <- factor(tad_K562_50kb$V1, levels = c(1:22))
tad_data_K562_50kb <- tad_K562_50kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1))
tad_data_K562_50kb$CL <- "K562"

tad_data_50kb <- rbind.data.frame(tad_data_gm12878_50kb, tad_data_K562_50kb)
tad_data_50kb$CL <- factor(tad_data_50kb$CL, levels=c("GM12878", "K562"))

p_tadnum_50kb <- ggplot(tad_data_50kb, aes(x=V1, y=Count, fill=CL))+
  geom_bar(stat="identity") +
  scale_fill_discrete(name="Cell Line") +
  #guides(fill=FALSE) +
  #ylab("Number of TADs") +
  #xlab("Chromosome") +
  ylab("") +
  xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

##100kb

```{r}
tad_gm12878_100kb <- read.table("Z:/TAD_data_analysis/GM12878/100kb/GM12878_domain_data_100000.b.txt")
tad_gm12878_100kb <- tad_gm12878_100kb[,1:3]
tad_gm12878_100kb <- tad_gm12878_100kb %>%
  group_by(V1) %>%
  mutate(Length = V3-V2)
tad_gm12878_100kb$V1 <- factor(tad_gm12878_100kb$V1, levels = c(1:22))
tad_data_gm12878_100kb <- tad_gm12878_100kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1)) 
tad_data_gm12878_100kb$CL <- "GM12878"

tad_K562_100kb <- read.table("Z:/TAD_data_analysis/K562/100kb/K562_domain_data_100000.b.txt")
tad_K562_100kb <- tad_K562_100kb[,1:3]
tad_K562_100kb <- tad_K562_100kb %>%
  group_by(V1) %>%
  mutate(Length = V3-V2)
tad_K562_100kb$V1 <- factor(tad_K562_100kb$V1, levels = c(1:22))
tad_data_K562_100kb <- tad_K562_100kb %>% 
  group_by(V1) %>% 
  summarise(Count = length(V1))
tad_data_K562_100kb$CL <- "K562"

tad_data_100kb <- rbind.data.frame(tad_data_gm12878_100kb, tad_data_K562_100kb)
tad_data_100kb$CL <- factor(tad_data_100kb$CL, levels=c("GM12878", "K562"))

p_tadnum_100kb <- ggplot(tad_data_100kb, aes(x=V1, y=Count, fill=CL))+
  geom_bar(stat="identity") +
  scale_fill_discrete(name="Cell Line") +
  #guides(fill=FALSE) +
  #ylab("Number of TADs") +
  #xlab("Chromosome") +
  ylab("") +
  xlab("") +
  theme_bw() +
  theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

##Plots

```{r}
figure <- ggarrange(p_tadnum_10kb,
                    p_tadnum_25kb,
                    p_tadnum_50kb,
                    p_tadnum_100kb,
                    ncol=2,
                    nrow=2,
                    common.legend = TRUE,
                    legend="top",
                    labels = "AUTO",
                    font.label = list(size=20))
figure
annotate_figure(figure,
    bottom = text_grob("Chromosome", color = "black", size = 20),
    left = text_grob("Number of TADs", color = "black", rot = 90, size=20)
)

### 2019-04-21 Scripts/evaluating_variable_importances.Rmd
editted results scripts

>>>>

#Variable Importance Heatmaps (actual importance values)

## SMOTE; distance types

### GM12878

```{r}
rfimpvars_gm12878_10kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
rfimpvars_gm12878_25kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
rfimpvars_gm12878_50kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
rfimpvars_gm12878_100kb_SMOTE <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")

vim.gm12878.smote <- vim.gm12878.smote[order(vim.gm12878.smote$Importance.10kb, decreasing = TRUE),]

vim.gm12878.smote.melt <- melt(vim.gm12878.smote)
vim.gm12878.smote.melt$Feature <- factor(vim.gm12878.smote.melt$Feature, levels = vim.gm12878.smote$Feature)

p.vim.gm12878 <- ggplot(vim.gm12878.smote.melt, aes(variable, 
                                                    ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("Resolution") +
  ylab("Genomic Annotation") +
  scale_fill_gradient2(low = "white",
                      mid = "pink",
                      midpoint = 50,
                      high = muted("red"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 5),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))
```

### K562

```{r}
rfimpvars_K562_10kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
rfimpvars_K562_25kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
rfimpvars_K562_50kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")
rfimpvars_K562_100kb_SMOTE <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/ENET/RF/rfimpvars.rds")

vim.K562.smote <- vim.K562.smote[order(vim.K562.smote$Importance.10kb, decreasing = TRUE),]

vim.K562.smote.melt <- melt(vim.K562.smote)
vim.K562.smote.melt$Feature <- factor(vim.K562.smote.melt$Feature, levels = vim.K562.smote$Feature)

p.vim.K562 <- ggplot(vim.K562.smote.melt, aes(variable, 
                                                    ordered(Feature, levels=rev(unique(Feature))))) + 
  geom_tile(aes(fill = value), colour = "white") + 
  xlab("Resolution") +
  ylab("Genomic Annotation") +
  scale_fill_gradient2(low = "white",
                      mid = "pink",
                      midpoint = 50,
                      high = muted("red"),
                      na.value = "grey50",
                      name="Predictive\nImportance") +
  scale_x_discrete(labels=c("10 kb", "25 kb", "50 kb", "100 kb"))+
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 5),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))
```
